ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-07-24 pyked.tex
fixed abstract

%====================================================================
\begin{abstract} % not to exceed 200 words
Fundamental experimental measurements of quantities including ignition delay times,
laminar flame speeds, and species profiles serve important roles in understanding
fuel chemistry and validating chemical kinetic models. However, despite both the
importance and abundance of such information in the literature, the community lacks
a widely adopted standard format for this data. This impedes both sharing and wide
use by the community. In this talk, we will introduce a new Chemical Kinetics
Experimental Data format, ChemKED, and the related Python-based package for creating
and validating ChemKED-formatted files called PyKED. We will also review past and
related efforts, and motivate the need for a new solution. ChemKED currently supports
the representation of autoignition delay time and laminar flame speed measurements.
ChemKED-formatted files contain all of the information needed to simulate experimental
data points, including the uncertainty of the data. ChemKED is based on the YAML data
serialization language, and is intended as a human- and machine-readable standard for
easy creation and automated use.
Development of ChemKED and PyKED occurs openly on GitHub under the
BSD 3-clause license, and contributions from the community are welcome. Plans for
future development include support for experimental data from jet stirred reactor,
extinction, and speciation measurements.
\end{abstract}

@@

ChemKED files are stored online in a git repository hosted on GitHub.
\footnote{\url{https://github.com/pr-omethe-us/ChemKED-database}}
Submissions from the community are welcomed and can be made via the standard Pull Request
on GitHub. The authors also encourage questions and problems to be submitted either via
email or as Issues on GitHub. In particular, researchers interested in converters for
internal data formats to the ChemKED format are encouraged to reach out. In addition,
converters to and from the ReSpecTh format are available in the PyKED repository.

>>>>

%====================================================================
\begin{abstract} % not to exceed 200 words
Fundamental experimental measurements of quantities including ignition delay times,
laminar flame speeds, and species profiles serve important roles in understanding
fuel chemistry and validating chemical kinetic models. However, despite both the
importance and abundance of such information in the literature, the community lacks
a widely adopted standard format for this data. This impedes both sharing and wide
use by the community. Here we introduce a new chemical kinetics
experimental data format, ChemKED, and the related Python-based package for creating
and validating ChemKED-formatted files called PyKED. We also review past and
related efforts, and motivate the need for a new solution. ChemKED currently supports
the representation of autoignition delay time measurements from shock tubes and rapid
compression machines.
ChemKED-formatted files contain all of the information needed to simulate experimental
data points, including the uncertainty of the data. ChemKED is based on the YAML data
serialization language, and is intended as a human- and machine-readable standard for
easy creation and automated use.
Development of ChemKED and PyKED occurs openly on GitHub under the
BSD 3-clause license, and contributions from the community are welcome. Plans for
future development include support for experimental data from laminar flame,
jet stirred reactor, and speciation measurements.
\end{abstract}

@@

\ck{} files are stored online in a git repository hosted on GitHub.
\footnote{\url{https://github.com/pr-omethe-us/ChemKED-database}}
Submissions from the community are welcomed and can be made via the standard Pull Request
on GitHub. The authors also encourage questions and problems to be submitted either via
email or as Issues on GitHub. In particular, researchers interested in converters for
internal data formats to the \ck{} format are encouraged to reach out. In addition,
the \pk{} package (described in more detail in Sec.~\label{sec:pyked-architecture})
provides converters to and from the ReSpecTh format~\autocite{Varga2015b}.
